Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
Paper stuff

We use the method of Contrastive Estimation \citep{Smith05} and substitute the space of all strings $\Sigma^*$ with neighbors of each word, $N(w)$. Toward this end, we transpose pairs of consecutive letters of $w$ near both ends of the word. We also do both simultaneously. Together these form our set of neighbors for $w$. The neighbors form a proxy for $\Sigma^*$, and represent the set of strings we want to reduce the probability of seeing in our model because they are not observed. This has the benefit of providing contrast in the structure of words while not requiring the model to look at the entire $\Sigma^*$.

@@

We optimize $L_L(\theta; D)$ with its gradient using the LBFGS-B algorithm.

@@

Additionally, we extend our feature set with features regarding the translation link between
the word and potential parent, to include information such as whether or not each candidate was
generated by a Turkish translation (a strong indicator for parent-ness) and how confident
the Turkish model was in selecting a parent.

Therefore, our model becomes:
\begin{equation}
    \begin{split}
        P(w) &= \sum_{z \in C'(w)} P(w,z) \\
             &= \frac{\sum_{z \in C'(w)} e^{\theta \cdot \phi(w, z, T(w), T(z))}}{\sum_{w' \in N(w)} \sum_{z \in C'(w')} e^{\theta \cdot \phi(w', z', T(w'), T(z'))}}
    \end{split}
\end{equation}
where $C'(w)$ is the potential parents of $w$ updated with potential irregular translations,
and $T(w)$ is the set of Turkish translations of $w$.

@@

We tested on 4 different sizes of wordvectors:
of wordvector 
small is 2.5k
med is 
large is 160k
full is 878k TODO

@@

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & \citeauthor{Narasimhan15} & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised (Baseline) & -  & - & - \\ 
            English & Semi-supervised & - & - & - \\ 
                    & Two language unsupervised & - & - & - \\ 
                    & Two language semi-supervised & - & - & - \\ \hline
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised (Baseline) & - & - & - \\ 
            Turkish & Semi-supervised & - & - & -  \\ 
                    & Two language unsupervised  & - & - & -  \\ 
                    & Two language semi-supervised  & - & - & -  \\ \hline
        \end{tabular}
        \caption{Accuracies of Various Models}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffet/ed & invalidated  & in/validat/ed & in/valid/at/ed \\ 
                    & ewers' &  ewer/s/' & dutifully & dutiful/ly & duti/ful/ly\\ 
                    & yowling & yowl/ing & ignominiously & ignominious/ly& ignomni/ous/ly \\ 
            \hline
                    & - & - & - & - & -\\ 
            Turkish & - & - & - & - & -\\ 
                    & - & - & - & - & -\\ 
                    & - & - & - & - & -\\ \hline
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
    English (dual-language) & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ \hline
                \end{tabular}
        \caption{Examples of Correct and Incorrect Segmentations}
    \end{center}
\end{table*}

@@

We found that adding the additional Turkish candidates and features regarding translation
did not help accuracy of training very much; this is likely due to the incompleteness of the translation
dictionary only being able to provide potential translations for very few words, and due to the ambiguity
of translation, it's very hard to tell whether or not something would make a good parent of a word after
translating the word into Turkish, taking the parent in Turkish, and translating it back.
\bibliography{paper}
\bibliographystyle{plainnat}

>>>>

We use the method of Contrastive Estimation (Smith and Eisner, 2005) and substitute the space of all strings $\Sigma^*$ with neighbors of each word, $N(w)$. Toward this end, we transpose pairs of consecutive letters of $w$ near both ends of the word. We also do both simultaneously. Together these form our set of neighbors for $w$. The neighbors form a proxy for $\Sigma^*$, and represent the set of strings we want to reduce the probability of seeing in our model because they are not observed. This has the benefit of providing contrast in the structure of words while not requiring the model to look at the entire $\Sigma^*$.

@@

We maximize $L_L(\theta; D)$ with its gradient using the LBFGS-B algorithm (Byrd et al., 1995).

@@

Additionally, we extend our feature set to include whether or not each candidate was
generated by a Turkish translation (a strong indicator for parent-ness) and how confident
the Turkish model was in selecting a parent.

@@

We tested on 4 different sizes of wordvectors:
of wordvector 
small is 2.5k
med is 
large is 160k
full is 878k

@@

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & \citeauthor{Narasimhan15} & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised (Baseline) & 0.664  & 0.649 & 0.656 \\ 
            English & Semi-supervised ($\lambda=15$) & 0.892 & 0.762 & 0.822 \\ 
                    & Two language unsupervised & 0.432 & 0.652 & 0.520 \\ 
                    & Two language semi-supervised & 0.449 & 0.759 & 0.564 \\ \hline
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised (Baseline) & 0.675 & 0.371 & 0.479 \\ 
            Turkish & Semi-supervised ($\lambda=50$) & 0.763 & 0.642 & 0.697 \\ 
        \end{tabular}
        \caption{Accuracies of Various Models}
    \end{center}
\end{table*}

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l | l |}
            \hline
            Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
                     & Word & Segmentation & Word & Predicted & Correct\\ \hline
            English & suburbanite & suburb/an/ite & provokingly & provok/ing/ly & provoking/ly  \\ 
                    & buffeted & buffet/ed & invalidated  & in/validat/ed & in/valid/at/ed \\ 
                    & ewers' &  ewer/s/' & dutifully & dutiful/ly & duti/ful/ly\\ 
                    & yowling & yowl/ing & ignominiously & ignominious/ly& ignomni/ous/ly \\ 
            \hline
                    & müzisyenlerinden & müzisyen/ler/i/nden & - & - & -\\ 
            Turkish & - & - & - & - & -\\ 
                    & - & - & - & - & -\\ 
                    & - & - & - & - & -\\ \hline
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
    English (dual-language) & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ 
                    & - & - & - & -  & -\\ \hline
                \end{tabular}
        \caption{Examples of Correct and Incorrect Segmentations}
    \end{center}
\end{table*}

@@

We found that adding the additional Turkish candidates and features were actually detrimental to the 
unsupervised case

\bibliography{paper}
\bibliographystyle{plainnat}
